# Preliminary Results

Experiment details:

* **"tableTalk?"** is always true. 
    + It means people can only interact when they are at part of the discussion group.

* **"recomputePreference?"** is always true
    + When people talk at the table, they can change their positions.
    
* **"strategy"** can be: "bridge" "random" "closeness" "influential"
    + This is how you select a person to be at the table, according to this value within the network.
    
* **"firstAgree?"** can be false or true
    + If the people invited in the first round (one per group) agree by default.
    
* **"invite?"** is always true
    + Anybody at the table can invite.

* **"InitialReach"** could be 5 10 15
    + The bigger the value the more coonected the network
    
* **"friendOfFriends?"** is always true
    + People at the table can invite friends of friends.

* **"Groups"** could be 3 6 9
    + Number of initial groups
    
* **"biasJoe"** can be "Own" "GovAndOwn" "AsGov"
    + Strategy that the people at the table follow when inviting.
    
* **"PopStakeholders"** could be 100 200 300.
    + Population in the simulation (without the government, one node).

<font color="red">The output variables are:</font>

* <font color="red">MaxSupport:</font>
    + The max level of support that a community reached during one simulation run.
    
* <font color="red">MaxMoment:</font>
    + The moment when the max level of support was reached.

**Each combination has been repeated only 10 times** (6480 runs), the preliminay results follow:

```{r, eval=TRUE, echo=FALSE, message=FALSE}
setwd("~/Documents/Evans/craig/abm")
res=read.csv("res10.csv",skip = 6)
library(magrittr)
library(dplyr)
library(ggplot2)

resNew=as.data.frame(res %>% group_by(X.run.number.) %>% filter(X.step. == max(X.step.)))
```

```{r, eval=TRUE, echo=FALSE, message=FALSE, fig.height=6,fig.width=8}

p <- ggplot(resNew, aes(strategy, maxsupport)) + geom_boxplot()
p + facet_grid(PopStakeholders ~ Groups) + 
  labs(title = "Distribution of Support per Strategy\n organized by Population & Groups")

```
```{r, eval=TRUE, echo=FALSE, message=FALSE, fig.height=6,fig.width=8}

ggplot(resNew, aes(maxsupport)) +  geom_histogram() + facet_grid(PopStakeholders ~ Groups) + 
  labs(title = "Distribution of Support organized by Population & Groups")

```

```{r, eval=TRUE, echo=FALSE, message=FALSE, fig.height=6,fig.width=8}
p <- ggplot(resNew, aes(maxmoment, maxsupport)) + geom_point()
p + facet_grid(PopStakeholders ~ Groups) + 
  labs(title = "Relationship of support and max moment \n organized by Population & Groups")
```


